The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-04 paper.tex
update

\section{Results}
\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
             indicating the dense disc is crucial for\
             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

>>>>

\section{Results}
\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
             indicating the dense disc is crucial for\
             the axis-symmetrical outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}
